---
title: "The NBA in Google Trends"
author: "Philip Petersen"
date: "29 november 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, tidy = TRUE, tidy.opts=list(width.cutoff= 80))
```

## The NBA
This paper is about the NBA in Google Trends.

```{r packages, include=FALSE}
library(gtrendsR)
library(ggplot2)
library(tidyverse)
```

Firstly, I am downloading the dataset for the NBA inside the gtrend package. 

```{r gtrend, include=FALSE}
nba.trend <- gtrends(c("nba"), gprop = "web", time = "all")[[1]]
class(nba.trend)
head(nba.trend)
```

Now I plot the data. 

```{r plot, echo=FALSE}
ggplot(data = nba.trend) + geom_line(mapping = aes(x= date, y = hits))
```

The number of hits over time is drastically decreasing and increasing. This is because there is a summer break in the NBA season. 

Let's take a look at the number of hits over time after The Golden State Warriors won the championship in the summer of 2015. 

```{r golden state, echo=FALSE}
ggplot(data = nba.trend) + 
  geom_line(mapping = aes(x= date, y = hits)) +
  geom_vline(xintercept = as.Date("2015-06-20"), color = "red")
```

After the championship of The Golden State Warriors in the NBA season 2015, the number of hits in the NBA have increased. 
